---
title: "Bikeshare_git3"
output: html_document
editor_options:
  chunk_output_type: console
---

### What are the most common route combinations in each city?

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
### Group each city dataset by start and end station; count number of occurrences for grouped values; arrange from greatest to least.

chi %>%
  group_by(chi$Start.Station, chi$End.Station) %>%
    summarize(count = n()) %>%
    arrange(desc(count))

ny %>%
  group_by(ny$Start.Station, ny$End.Station) %>%
    summarize(count = n()) %>%
    arrange(desc(count))

dc %>%
  group_by(dc$Start.Station, dc$End.Station) %>%
    summarize(count = n()) %>%
    arrange(desc(count))
```

### In Chicago, the most frequent route is from 'Lake Shore Dr & Monroe St' to 'Streeter Dr & Grand Ave'; this makes intuitive sense because of the stations' proximity to Chicago's popular Grant Park and Navy Pier. In New York, it's 'E 7 St & Avenue A' to 'Cooper Square & E 7 St'; perhaps many tourists are traveling from Tompkins Square Park to Cooper Square. Lastly, DC's most frequented route is a round trip from the 'Jefferson Dr & 14th St SW' Station; it is located in the heart of the National Mall, one of the most visited sites in the country.
