---
title: "Bikeshare_git1"
output: html_document
editor_options: 
  chunk_output_type: console
---
### Question 1: In descending order from greatest to smallest, what was the relative variability of the three cities trip durations

library(ggplot2)
library(ggthemes)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '~/R')
```

```{r}
chi <- read.csv('chicago.csv', sep = ',')
ny <- read.csv('new-york-city.csv', sep = ',')
dc <- read.csv('washington.csv', sep = ',')
```

```{r}
### Check summary statistics for Trip.Duration to determine scope of the data.
summary(chi$Trip.Duration)
summary(ny$Trip.Duration)
summary(dc$Trip.Duration)
```

```{r}
### Calculate 99th percentile for each cities' Trip.Duration to identify outlier values.
quantile(chi$Trip.Duration, probs = .99)
quantile(ny$Trip.Duration, probs = .99)
quantile(dc$Trip.Duration, probs = .99)
```

```{r}
### Create new subsets of the data with values for Trip.Duration approximately below the 99th percentile to remove outliers.
chi2 <- chi[chi$Trip.Duration < 5100,]
ny2 <- ny[ny$Trip.Duration < 3400,]
dc2 <- dc[dc$Trip.Duration < 8600,]
```

```{r}
### Create boxplots of the modified Trip.Duration values and zoom in between values of 0 and 2000 to compare IQRs for each city; add an hline for std dev.

ggplot(aes(y = Trip.Duration), data = chi2) +
  geom_boxplot() +
  geom_hline(yintercept = sd(chi2$Trip.Duration), color = 'blue') +
  coord_cartesian(ylim = c(0,2000)) +
  ggtitle('Chicago Trip Duration Boxplot') +
  labs(x = 'Trip Duration', y = 'IQR + Median')

ggplot(aes(y = Trip.Duration), data = ny2) +
  geom_boxplot() +
  geom_hline(yintercept = sd(ny2$Trip.Duration), color = 'blue') +
  coord_cartesian(ylim = c(0,2000)) +
  ggtitle('New York Trip Duration Boxplot') +
  labs(x = 'Trip Duration', y = 'IQR + Median')

ggplot(aes(y = Trip.Duration), data = dc2) +
  geom_boxplot() +
  geom_hline(yintercept = sd(dc2$Trip.Duration), color = 'blue') +
  coord_cartesian(ylim = c(0,2000)) +
  ggtitle('Washington Trip Duration Boxplot') +
  labs(x = 'Trip Duration', y = 'IQR + Median')
```

```{r}
### Calculate standard deviations to determine base variability.
sd(chi2$Trip.Duration)
sd(ny2$Trip.Duration)
sd(dc2$Trip.Duration)
```

```{r}
### Calculate coefficients of variation for subsets to obtain variability relative to mean values.
sd(chi2$Trip.Duration)/mean(chi2$Trip.Duration)
sd(ny2$Trip.Duration)/mean(ny2$Trip.Duration)
sd(dc2$Trip.Duration)/mean(dc2$Trip.Duration)
```

### It appears from the standard deviations calculated for each city's adjusted trip durations that Washington has the greatest variability, followed by Chicago, and New York. Calculating the coefficient of variation, the gap between variablity does seem to shrink somewhat, suggesting that the standard deviation is somewhat equalized when taking into account average trip durations by city. Boxplots for each city also reveal Washington with the greatest variability and New York with the least, taking the size of IQR as a proxy for variability.
