---
title: "Bikeshare_git2"
output: html_document
editor_options:
  chunk_output_type: console
---

### Which month has the highest share of customer users for each city? Which
### month has the lowest share of subscriber users for each city?

library(dplyr)
library(stringr)
library(magrittr)
library(scales)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
### Call tables for each dataset's User.Type to view composition.

table(chi$User.Type)
table(ny$User.Type)
table(dc$User.Type)
```

```{r}
### Create new field for start month for each city.

chi$start.month <- str_sub(chi$Start.Time,6,7)
ny$start.month <- str_sub(ny$Start.Time,6,7)
dc$start.month <- str_sub(dc$Start.Time,6,7)
```

```{r}
### Plot bar graphs of proportions of customer vs. subscriber user types; wrap on start month; add text of user type percentages.

ggplot(aes(x = User.Type, group = start.month), data = subset(chi, User.Type != 'Dependent')) +
  geom_bar(aes(y = ..prop..)) +
  geom_text(aes(label = scales::percent(..prop..), y = ..prop..), stat = 'count', vjust = -.5) +
    facet_wrap(~start.month) +
      labs(x = 'User Type', y = 'User Share', title = 'Chicago Users by Month')

ggplot(aes(x = User.Type, group = start.month), data = subset(ny, User.Type == 'Subscriber' | User.Type == 'Customer')) +
  geom_bar(aes(y = ..prop..)) +
  geom_text(aes(label = scales::percent(..prop..), y = ..prop..), stat = 'count', vjust = -.5) +
    facet_wrap(~start.month) +
      labs(x = 'User Type', y = 'User Share', title = 'New York Users by Month')

ggplot(aes(x = User.Type, group = start.month), data = dc) +
  geom_bar(aes(y = ..prop..)) +
  geom_text(aes(label = scales::percent(..prop..), y = ..prop..), stat = 'count', vjust = -.5) +
    facet_wrap(~start.month) +
      labs(x = 'User Type', y = 'User Share', title = 'Washington Users by Month')
```

### By splitting the month from the 'Start.Time' field, we can look at user type usage on a proportional basis in each city. After facet wrapping, we see in Chicago that Customers had the greatest share of usage in June with 26.15% of ridership. In New York and Washington, however, Customers' top usages as a share of users both came in April, with 14.36% and 33.82% respectively. Conversely, the months containing the lowest share of 'subscriber' usage match the same ones as mentioned above.
